A Greedy Framework for First-Order Optimization

### 2013-12-02 nips/paper.tex
small fixes to nips paper

\paragraph{Primal vs. dual algorithms.}
It is worth taking a moment to contrast the primal and dual algorithms. Note 
that \emph{both} algorithms have a primal convergence guarantee (i.e. both 
guarantee that $\hat{u}_T$ is close to optimal). The sense in which the latter 
algorithm is a ``dual'' algorithm is that it hinges on strong convexity of 
the dual, as opposed to strong convexity of the primal. If we care about dual 
convergence instead of primal convergence, the only change we need to make 
is to take $\hat{\theta}_T$ at the end of the algorithm instead of $\hat{u}_T$. 
(This can be seeing by defining the loss function $L_2(\theta, u) \eqdef -L(u, \theta)$, 
which inverts the role of $u$ and $\theta$ but yields the same updates as above.)

@@

\paragraph{Acknowledgements.}
Thanks to Simon Lacoste-Julien, Martin Jaggi, Percy Liang, Arun Chaganty, and Sida Wang 
for helpful discussions. Thanks also to the anonymous reviewer for suggesting improvements 
to the paper. This work was supported by the Hertz Foundation and by the NDSEG graduate 
fellowship.

>>>>

\paragraph{Primal vs. dual algorithms.}
It is worth taking a moment to contrast the primal and dual algorithms. Note 
that \emph{both} algorithms have a primal convergence guarantee (i.e. both 
guarantee that $\hat{u}_T$ is close to optimal). The sense in which the latter 
algorithm is a ``dual'' algorithm is that it hinges on strong convexity of 
the dual, as opposed to strong convexity of the primal. If we care about dual 
convergence instead of primal convergence, the only change we need to make 
is to take $\hat{\theta}_T$ at the end of the algorithm instead of $\hat{u}_T$. 
(This can be seeing by defining the loss function $L'(\theta, u) \eqdef -L(u, \theta)$, 
which inverts the role of $u$ and $\theta$ but yields the same updates as above.)

@@

\paragraph{Acknowledgements.}
Thanks to Cameron Freer, Simon Lacoste-Julien, Martin Jaggi, Percy Liang, Arun Chaganty, and Sida Wang 
for helpful discussions. Thanks also to the anonymous reviewer for suggesting improvements 
to the paper. JR was supported by the Hertz Foundation. JHH was supported by the U.S. Government under FA9550-11-C-0028 and awarded by the Department of Defense, Air Force Office of Scientific Research, National Defense Science and Engineering Graduate (NDSEG) Fellowship, 32 CFR 168a.
fellowship.
